Human Pose Estimation for Video Game Control

### 2022-05-08 paper/paper.tex
minor typo change in feature tracking for chrome dino game
added game interface section

\begin{enumerate}
    \item For every frame of video, compute $y_t$, the midpoint of all keypoints 
        existing in the frame from the set 
        \{left eye, right eye, left ear, right ear, nose\}.
    \item Compute $y'_t$, the difference of $y_t$ and $y_{t-1}$.
    \item If $y'_t > 10, y'_{t-1} < 10, y'_{t-2} < 10$ and $y'_{t-3} < 10$: 
        Classify current frame as a duck.
    \item If $y'_t < 10, y'_{t-1} < 10, y'_{t-2} < 10$ and $y'_{t-3} < 10$:
        Classify current frame as a jump.
    \item If none of the above conditions are satisfied, classify current frame as 
        no command.
\end{enumerate}

@@

\subsection{Game Interface}

>>>>

\begin{enumerate}
    \item For every frame of video, compute $y_t$, the midpoint of y-components 
    of all keypoints 
        existing in the frame from the set 
        \{left eye, right eye, left ear, right ear, nose\}.
    \item Compute $y'_t$, the difference of $y_t$ and $y_{t-1}$.
    \item If $y'_t > 10, y'_{t-1} < 10, y'_{t-2} < 10$ and $y'_{t-3} < 10$: 
        Classify current frame as a duck.
    \item If $y'_t < 10, y'_{t-1} < 10, y'_{t-2} < 10$ and $y'_{t-3} < 10$:
        Classify current frame as a jump.
    \item If none of the above conditions are satisfied, classify current frame as 
        no command.
\end{enumerate}

@@

\subsection{Game Interface}
The final step before our human-computer interaction system is fully functional 
is to simulate keypresses to play the two example games selected. In this project 
we select simple example games that can be run on the Jetson Nano within a browser 
or through pyGame. However, the system was designed so that during this phase, the 
Jetson Nano will send data to a game console machine either through serial 
communication or wirelessly through bluetooth/wifi communication to play more 
intensive games on a dedicated machine.\\

In order to simulate keypresses, we utilize a Python package known as pynput, 
which allows us to press and release arrow keys at the appropriate times in order 
to simulate keypresses to the example video games.
